---
title: "Playgrounds Spatial Analysis"
output: html_document
---

Outline of analysis:

1. Load libraries and data (Line 17-31)
2. Set up MapBox token (Line 35-39)
3. Create isochrones for walking, cycling, and driving (Line 43-70)
4. Plot isochrones on a map with population data (Line 73-102)
5. Calculate statistics for cycling isochrones (Line 110-236)
6. Calculate statistics for walking isochrones (Line 243-361)
7. Calculate playground statistics (Line 368-448)
8. Compare cycling and walking statistics (Line 452-562)

```{r setup}
library(sf)
library(dplyr)
library(leaflet)
library(ggplot2)
library(mapboxapi)
library(tidyr)
```

```{r}
playgrounds <- readRDS("data/playgrounds_clean.rds")
muni_income <- readRDS("data/muni_income.rds")
muni_population <- readRDS("data/muni_population.rds")

```

# MapBox Setup

```{r}
my_token <- "pk.eyJ1IjoibWF0aWxkYXNpZiIsImEiOiJjbTl2MzF0NWowZGdvMmpyMmxjbDRmZTA3In0.cELeKMY07SV3Z37zMLBIOQ"

mb_access_token(my_token, install = TRUE, overwrite = TRUE)
```


# CREATE ISOCHRONES
```{r}
# Use playgrounds df as the data focus sf object
playgrounds <- st_as_sf(playgrounds, coords = c("longitude", "latitude"), crs = 4326)

# walking isos
walking_isos <- mb_isochrone(
  playgrounds,
  profile = "walking",
  time = 5,
  id = "adresse"
  )

# cycling isos
cycling_isos <- mb_isochrone(
  playgrounds,
  profile = "cycling",
  time = 5,
  id = "adresse"
  )

# driving isos
driving_isos <- mb_isochrone(
  playgrounds,
  profile = "driving",
  time = 5,
  id = "adresse"
  )
```

## PLOT ALL ISOCHRONES
```{r}
pal <- colorBin(palette = "OrRd", domain = muni_population$child_population, bins = 8)

leaflet(muni_population) %>%
  addProviderTiles("CartoDB.Positron") %>%
  # add population
  addPolygons(fillColor = ~pal(child_population),
              color = "#444444",
              weight = 1,
              fillOpacity = 0.3,
              popup = ~paste(municipality, "<br>Child Population:", child_population)) %>%
  addLegend(pal = pal, values = ~child_population, opacity = 0.5,
            title = "Child Population",
            position = "bottomright") %>% 
# uncomment code below to add cycling isochrones
    # addPolygons(data = cycling_isos,   
    #           fillColor = "dodgerblue",
    #           fillOpacity = 0.3,
    #           stroke = FALSE) %>%
    addPolygons(data = walking_isos,
              fillColor = "deeppink",
              fillOpacity = 0.4,
              stroke = FALSE) %>% 
    # add playground markers
  addCircleMarkers(data = playgrounds, lng = ~longitude, lat = ~latitude, radius = 0.1,
                   label = ~paste(municipality),
                   color = "darkblue", fillOpacity = 1) %>% 
    addScaleBar(position = "topright", options = scaleBarOptions(metric = TRUE, imperial = FALSE))

```




# CYCLING - CALCULATE STATS

## DATA PREPARATION
```{r}
# select only needed municipalities
muni_population2 <- muni_population %>% 
  filter(municipality %in% c("Aarhus", "Frederiksberg", "Koebenhavn", "Ringkoebing Skjern", "Silkeborg", "Vesthimmerland"))

cycling_geo <- st_geometry(cycling_isos)

st_crs(muni_population2)
st_crs(cycling_geo)

# st_transform cycling geo to match munipopulation
cycling_geo <- st_transform(cycling_geo, 4326)
st_crs(cycling_geo)

# geometry cycling isochrones
cycling_union <- st_union(cycling_geo)

# check classes
class(muni_population2)
class(cycling_union)
```

## CALCULATE CYCLING STATS
```{r}
# Intersect with municipalities
intersections <- st_intersection(muni_population2, cycling_union)

# Compute covered area in km² (convert explicitly)
intersections <- intersections %>%
  mutate(covered_area_km2 = as.numeric(st_area(geometry)) / 10^6) %>%
  st_drop_geometry() %>%
  group_by(municipality) %>%
  summarise(covered_area = sum(covered_area_km2), .groups = "drop")

# Calculate municipality area (in km²)
muni_population2 <- muni_population2 %>%
  mutate(total_area_km2 = as.numeric(st_area(geometry)) / 10^6)

# Prepare attribute-only data
muni_data <- muni_population2 %>%
  st_drop_geometry() %>%
  dplyr::select(municipality, child_population, total_area_km2)

# Join covered area
cycling_coverage_data <- left_join(muni_data, intersections, by = "municipality")


# Final calculations
cycling_coverage_data <- cycling_coverage_data %>%
  mutate(
    covered_area = pmin(covered_area, total_area_km2),
    uncovered_area = total_area_km2 - covered_area,
    child_density = child_population / total_area_km2,
    uncovered_child_count = child_density * uncovered_area,
#estimated number of children in the uncovered area (assuming uniform distribution)
    uncovered_pct = pmax(uncovered_area / total_area_km2) * 100,
    covered_pct = pmax(covered_area / total_area_km2) * 100,
    covered_child_count = child_density * covered_area,
    prop_children_covered = covered_child_count / child_population
  )


# join and pivot for income and transport mode plots
cycling_coverage_data <- left_join(cycling_coverage_data, muni_income, by = "municipality") %>% 
    st_drop_geometry() %>% 
    dplyr::select(-contains("geometry"))


cycling_coverage_pivot <- cycling_coverage_data %>%
  mutate(income_quantile = ntile(income, 4)) %>%  # Divide into 4 income groups
  tidyr::pivot_longer(cols = c(covered_area, uncovered_area), 
               names_to = "coverage_type", values_to = "area")


# save cycling data
write.csv(cycling_coverage_data, "output/cycling_stats/cycling_coverage_data.csv", row.names = FALSE)

```

## PLOT CYCLING STATS
```{r}
# 1. Uncovered area percentage
p1 <- ggplot(cycling_coverage_data, aes(x = reorder(municipality, -uncovered_pct), y = uncovered_pct, fill = municipality)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "5min Cycling Isochrone: Uncovered Area Percentage by Municipality",
       x = "Municipality", y = "Uncovered Area (%)") +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("output/cycling_stats/1_uncovered_area_pct.png", plot = p1, width = 8, height = 6)

# 2. Uncovered child density:  The number of children per square kilometer living in areas of a municipality that are not covered by  isochrones 
p2 <- ggplot(cycling_coverage_data, aes(x = reorder(municipality, -uncovered_child_count), y = uncovered_child_count, fill = municipality)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "5min Cycling Isochrone: Uncovered Child Count by Municipality",
       x = "Municipality", y = "Uncovered Child Count ") +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("output/cycling_stats/2_uncovered_child_count.png.png", plot = p2, width = 8, height = 6)

# 3. Child Population in pct
p3 <- ggplot(cycling_coverage_data, aes(x = reorder(municipality, -child_density), y = child_density, fill = municipality)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Child Population Density by Municipality",
       x = "Municipality", y = "Child Density") +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("output/cycling_stats/3_child_density.png", plot = p3, width = 8, height = 6)

# 4. Avg income by income quartile
p4 <- ggplot(cycling_coverage_pivot, aes(x = factor(income_quantile), y = area, fill = coverage_type)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(title = "Area Coverage by Income Quantile",
       x = "Income Quantile (1 = Lowest)", y = "Proportion of Total Area",
       fill = "Coverage Type") +
  theme_minimal()

ggsave("output/cycling_stats/4_income_quartile_coverage.png", plot = p4, width = 8, height = 6)

# 5. Covered area per municipality coloured by child density
p5 <- ggplot(cycling_coverage_data, aes(x = municipality)) +
  geom_col(aes(y = (100- uncovered_pct), fill = child_density)) +
  labs(title = "% Covered Area per Municipality", y = "% covered Area",) +
  theme_minimal()

ggsave("output/cycling_stats/5_covered_area_by_child_density.png", plot = p5, width = 8, height = 6)

# 6. Uncovered child count vs income
p6 <- ggplot(cycling_coverage_data, aes(x = income, y = uncovered_child_count, colour = municipality)) +
  geom_point(size = 3) +
  geom_smooth(method = lm, color = "red") +
  labs(title = "Uncovered Child Count vs Income",
       x = "Mean Income", y = "Children Outside Coverage Zone")

ggsave("output/cycling_stats/6_uncovered_child_vs_income.png", plot = p6, width = 8, height = 6)

```



# WALKING - CALCULATE STATS

## DATA PREPARATION
```{r}
# select only needed municipalities
muni_population2 <- muni_population %>% 
  filter(municipality %in% c("Aarhus", "Frederiksberg", "Koebenhavn", "Ringkoebing Skjern", "Silkeborg", "Vesthimmerland"))

walking_geo <- st_geometry(walking_isos)

st_crs(muni_population2)
st_crs(walking_geo)

# st_transform walking geo to match munipopulation
walking_geo <- st_transform(walking_geo, 4326)

st_crs(walking_geo)

# geometry walking isochrones
walking_union <- st_union(walking_geo)

class(muni_population2)
class(walking_union)
```

# CALCULATE WALKING STATS
```{r}
# Intersect with municipalities
walking_intersections <- st_intersection(muni_population2, walking_union)

# Compute covered area in km² (convert explicitly)
walking_intersections <- walking_intersections %>%
  mutate(covered_area_km2 = as.numeric(st_area(geometry)) / 10^6) %>%
  st_drop_geometry() %>%
  group_by(municipality) %>%
  summarise(covered_area = sum(covered_area_km2), .groups = "drop")

# Join covered area
walking_coverage_data <- left_join(muni_data, walking_intersections, by = "municipality")


# Final calculations
walking_coverage_data <- walking_coverage_data %>%
  mutate(
    covered_area = pmin(covered_area, total_area_km2),
    uncovered_area = total_area_km2 - covered_area,
    child_density = child_population / total_area_km2,
    uncovered_child_count = child_density * uncovered_area, # estimated number of children in the uncovered area (assuming uniform distribution)
    uncovered_pct = pmax(uncovered_area / total_area_km2) * 100,
    covered_pct = pmax(covered_area / total_area_km2) * 100,
    covered_child_count = child_density * covered_area,
    prop_children_covered = covered_child_count / child_population
  )

# join and pivtor data for plotting
walking_coverage_data_2 <- left_join(walking_coverage_data, muni_income, by = "municipality") %>% 
    st_drop_geometry() %>% 
    dplyr::select(-contains("geometry"))


walking_coverage_data_2_pivot <- walking_coverage_data_2 %>%
  mutate(income_quantile = ntile(income, 4)) %>%  # Divide into 4 income groups
  tidyr::pivot_longer(cols = c(covered_area, uncovered_area), 
               names_to = "coverage_type", values_to = "area")

# save walking data
write.csv(walking_coverage_data, "output/walking_stats/walking_coverage_data.csv", row.names = FALSE)

```


## PLOT WALKING STATS
```{r}
# 1. Uncovered area percentage
p7 <- ggplot(walking_coverage_data, aes(x = reorder(municipality, -uncovered_pct), y = uncovered_pct, fill = municipality)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "5min Walking Isochrone: Uncovered Area Percentage by Municipality",
       x = "Municipality", y = "Uncovered Area (%)") +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("output/walking_stats/1_uncovered_area_pct.png", plot = p7, width = 8, height = 6)

# 2 . Uncovered child density:  The number of children per square kilometer living in areas of a municipality that are not covered by isochrones 
p8 <- ggplot(walking_coverage_data, aes(x = reorder(municipality, -uncovered_child_count), y = uncovered_child_count, fill = municipality)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "5min Walking Isochrone: Uncovered Child Count by Municipality",
       x = "Municipality", y = "Uncovered Child Count ") +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("output/walking_stats/2_uncovered_child_count.png.png", plot = p8, width = 8, height = 6)

# 3. Child Density per municipality
p9 <- ggplot(walking_coverage_data, aes(x = reorder(municipality, -child_density), y = child_density, fill = municipality)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Child Population Density by Municipality",
       x = "Municipality", y = "Child Density") +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("output/walking_stats/3_child_density.png", plot = p9, width = 8, height = 6)


# 4. Avg income by income quartile
p10 <- ggplot(walking_coverage_data_2_pivot, aes(x = factor(income_quantile), y = area, fill = coverage_type)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(title = "5min Walking Isochrone: Area Coverage by Income Quantile",
       x = "Income Quantile (1 = Lowest)", y = "Proportion of Total Area",
       fill = "Coverage Type") +
  theme_minimal()

ggsave("output/walking_stats/4_income_quartile_coverage.png", plot = p10, width = 8, height = 6)

# 5. Covered area per municipality coloured by child density
p11 <- ggplot(walking_coverage_data, aes(x = municipality)) +
  geom_col(aes(y = covered_pct, fill = child_density)) +
  labs(title = "5min Walking Isochrone: Covered Area per Municipality", y = "% covered area",) +
  theme_minimal()

ggsave("output/walking_stats/5_covered_area_by_child_density.png", plot = p11, width = 8, height = 6)

# 6. Uncovered child density vs income
p12 <-  ggplot(walking_coverage_data_2, aes(x = income, y = uncovered_child_count, colour = municipality)) +
  geom_point(size = 4) +
  geom_smooth(method = "lm", color = "red") + 
  ylim(0,NA) +
  labs(title = "Estimated Child Population in Uncovered Areas by Income and Municipality",
       x = "Mean Income", y = "Estimated Child Population in Uncovered Areas")

ggsave("output/walking_stats/6_uncovered_child_vs_income.png", plot = p12, width = 8, height = 6)

```

# Plot Walking Isochrone with child density
```{r}

isochrone_density <- left_join(muni_population, walking_coverage_data, by = "municipality")

pal2 <- colorBin(palette = "OrRd", domain = isochrone_density$child_density, bins = 6)


leaflet(isochrone_density) %>%
  addProviderTiles("CartoDB.Positron") %>%
  # add population
  addPolygons(fillColor = ~pal2(isochrone_density$child_density),
              color = "white",
              weight = 1,
              fillOpacity = 0.3,
              popup = ~paste(municipality, "<br>Child Density:", child_density)) %>%
  addLegend(pal = pal2, values = ~child_density, opacity = 0.5,
            title = "Child Density",
            position = "bottomright") %>% 
# uncomment code below to add cycling isochrones
    # addPolygons(data = cycling_isos,   
    #           fillColor = "dodgerblue",
    #           fillOpacity = 0.3,
    #           stroke = FALSE) %>%
    addPolygons(data = walking_isos,
              fillColor = "deeppink",
              fillOpacity = 0.4,
              stroke = FALSE) %>% 
    # add playground markers
  addCircleMarkers(data = playgrounds, lng = ~longitude, lat = ~latitude, radius = 0.1,
                   label = ~paste(municipality),
                   color = "darkblue", fillOpacity = 1) %>% 
    addScaleBar(position = "topright", options = scaleBarOptions(metric = TRUE, imperial = FALSE))
```



# CALCULATE PLAYGROUND STATISTICS

## DATA PREPARATION
```{r}
# recode playground municipality names
playgrounds$municipality <- gsub("æ", "ae", playgrounds$municipality)
playgrounds$municipality <- gsub("Æ", "Ae", playgrounds$municipality)
playgrounds$municipality <- gsub("ø", "oe", playgrounds$municipality)
playgrounds$municipality <- gsub("å", "aa", playgrounds$municipality)
playgrounds$municipality <- gsub("Å", "Aa", playgrounds$municipality)
playgrounds$municipality <- gsub("-", " ", playgrounds$municipality)

# Spatial join to assign each playground to a municipality
playgrounds_in_munis <- st_join(playgrounds, muni_population2)

# Count playgrounds by municipality
playground_counts <- playgrounds_in_munis %>%
  st_drop_geometry() %>%
  count(municipality.x, name = "n_playgrounds") %>% 
  rename(municipality = municipality.x)


# Join with playground counts
coverage_stats <- left_join(walking_coverage_data, playground_counts, by = "municipality") %>%
  mutate(
    n_playgrounds = ifelse(is.na(n_playgrounds), 0, n_playgrounds),  # handle municipalities with 0 playgrounds
    playgrounds_per_km2 = n_playgrounds / total_area_km2,
    playgrounds_per_1000_children = n_playgrounds / (child_population / 1000)
  )

# join with income data
coverage_stats <- left_join(coverage_stats, muni_income, by = "municipality")

coverage_stats <- coverage_stats %>%
      mutate(income_quartile = ntile(income, 4))


# split density into quantiles
coverage_stats <- coverage_stats %>%
  mutate(density_quartile = ntile(child_density, 4))

# save walking data
write.csv(coverage_stats, "output/playground_stats/coverage_stats.csv", row.names = FALSE)
```

## PLOT PLAYGROUND STATS
```{r}
# 1. Number of playgrounds in each municipality
p13 <- ggplot(playground_counts, aes(x = reorder(municipality, -n_playgrounds), y = n_playgrounds, fill = municipality)) +
  geom_bar(stat = "identity") +
  labs(title = "Number of Playgrounds per Municipality",
       x = "Municipality",
       y = "Number of Playgrounds") +
  theme_minimal()

ggsave("output/playground_stats/playground_count.png", plot = p13, width = 8, height = 6)

# 2. Plot playgrounds per km²
p14 <-ggplot(coverage_stats, aes(x = reorder(municipality, -playgrounds_per_km2), y = playgrounds_per_km2, fill = municipality)) +
  geom_bar(stat = "identity") +
  labs(title = "Playgrounds per km² by Municipality",
       x = "Municipality",
       y = "Playgrounds per km²") +
  theme_minimal()

ggsave("output/playground_stats/playground_per_km2.png", plot = p14, width = 8, height = 6)

# 3. Plot playgrounds per 1,000 children
p15 <-ggplot(coverage_stats, aes(x = reorder(municipality, -playgrounds_per_1000_children), y = playgrounds_per_1000_children, fill = municipality)) +
  geom_bar(stat = "identity") +
  labs(title = "Playgrounds per 1,000 Children by Municipality",
       x = "Municipality",
       y = "Playgrounds per 1,000 Children") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("output/playground_stats/playgrounds_per_1000_children.png", plot = p15, width = 8, height = 6)

# No. uncovered children by Income Quantile
p16 <-ggplot(coverage_stats, aes(x = income_quartile, y = uncovered_child_count, fill = municipality)) +
  geom_bar(stat = "identity") +
  labs(title = "Estimated Proportion of Uncovered Children by Income Quartile",
       x = "Income Quartile", y = "Estimated proportion of uncovered children")

ggsave("output/playground_stats/uncovered_children_income_quartile.png", plot = p16, width = 8, height = 6)

# density quantiles
p17 <-ggplot(coverage_stats, aes(x = density_quartile, y = uncovered_child_count, fill = municipality)) +
  geom_bar(stat = "identity") +
  labs(title = "Estimated Proportion of Uncovered Children by Child Density Quartile",
       x = "Child Density Quartile", y = "Estimated Proportion of Uncovered Children")

ggsave("output/playground_stats/uncovered_children_density_quartile.png", plot = p17, width = 8, height = 6)

```


# COMPARING CYCLING v. WALKING STATS
```{r}
# select required columns and rename for clarity
cycling_covered <- cycling_coverage_data %>%
  dplyr::select(municipality, covered_pct, covered_child_count, uncovered_child_count) %>%
  rename(covered_pct_cycling = covered_pct,
        covered_child_count_cycling = covered_child_count,
        uncovered_child_count_cycling = uncovered_child_count)

walking_covered <- walking_coverage_data %>%
  dplyr::select(municipality, covered_pct, covered_child_count, uncovered_child_count) %>%
  rename(covered_pct_walking = covered_pct,
        covered_child_count_walking = covered_child_count,
        uncovered_child_count_walking = uncovered_child_count)

# join the dataframes
joined_covered <- left_join(cycling_covered, walking_covered, by = "municipality")

# Calculate percentage increase in coverage from walking to cycling
joined_covered <- joined_covered %>%
  mutate(
    pct_increase = ((covered_pct_cycling - covered_pct_walking) / covered_pct_walking) * 100
  )

# Reshape data for plotting
long_covered <- joined_covered %>%
    dplyr::select(municipality, covered_pct_walking, covered_pct_cycling) %>%
    pivot_longer(cols = starts_with("covered_pct"),
                 names_to = "mode",
                 values_to = "covered_pct") %>%
    mutate(mode = recode(mode,
                         "covered_pct_walking" = "Walking",
                         "covered_pct_cycling" = "Cycling"))
# Reshape uncovered child counts for plotting
uncovered_long <- joined_covered %>%
  select(municipality, uncovered_child_count_walking, uncovered_child_count_cycling) %>%
  pivot_longer(
    cols = starts_with("uncovered_child_count"),
    names_to = "mode",
    values_to = "uncovered_child_count"
  ) %>%
  mutate(mode = recode(mode,
                       "uncovered_child_count_walking" = "Walking",
                       "uncovered_child_count_cycling" = "Cycling"))

# save comparison data
write.csv(joined_covered, "output/comparison_stats/joined_covered.csv", row.names = FALSE)
```

## PLOT COMPARATIVE STATS
```{r}
# 1. Compare percentage increase in coverage from walking to cycling
p18 <- ggplot(joined_covered, aes(x = reorder(municipality, -pct_increase), y = pct_increase)) +
  geom_bar(stat = "identity", fill = "#FF5733") +
  labs(title = "Percentage Increase in Coverage from Walking to Cycling Isochrones",
       x = "Municipality",
       y = "Percentage Increase (%)") +
  theme_minimal()

ggsave("output/comparison_stats/pct_increase_coverage.png", plot = p18, width = 8, height = 6)

# 2. Compare % coverage from walking to cycling
p19 <- ggplot(long_covered, aes(x = reorder(municipality, -covered_pct), y = covered_pct, fill = mode)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.6) +
  labs(title = "Coverage Comparison: 5-minute Walking vs 5-minute Cycling Isochrones",
       x = "Municipality",
       y = "Coverage (%)",
       fill = "Mode") +
  scale_fill_manual(values = c("Walking" = "#3A86FF", "Cycling" = "#4C9F70")) +
  theme_minimal()+  
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("output/comparison_stats/coverage_comparison.png", plot = p19, width = 8, height = 6)

# 3. Compare estimated no. of children covered by walking v. cycling
p20 <- ggplot(uncovered_long, aes(x = reorder(municipality, -uncovered_child_count), y = uncovered_child_count, fill = mode)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.6) +
  labs(title = "Uncovered Children: 5-minute Walking vs 5-minute Cycling Isochrones",
       x = "Municipality",
       y = "Number of Uncovered Children",
       fill = "Mode") +
  scale_fill_manual(values = c("Walking" = "#3A86FF", "Cycling" = "#4C9F70")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("output/comparison_stats/uncovered_children_comparison.png", plot = p20, width = 8, height = 6)

# 4. Proportion of Uncovered Children by Child Density and Income
p21 <- ggplot(coverage_stats, aes(x = child_density, y = uncovered_child_count)) +
  geom_point(aes(color = as.factor(income_quartile)), size = 4, alpha = 0.7) +
  geom_text(aes(label = municipality), vjust = -1, size = 3) +
  scale_color_brewer(palette = "Set2", name = "Income Quartile") +
  labs(
    title = "Proportion of Uncovered Children by Child Density and Income",
    x = "Child Density (children per km²)",
    y = "Proportion of Uncovered Children"
  ) 

ggsave("output/comparison_stats/proportion_uncovered_children_density_income.png", plot = p21, width = 8, height = 6)

# 5. Uncovered Children by Income Quantile and Child Density
p22 <- ggplot(coverage_stats, aes(x = as.factor(income_quartile), y = uncovered_child_count)) +
  geom_point(aes(size = child_density, color = as.factor(income_quartile)), alpha = 1) +
  geom_text(aes(label = municipality), vjust = -1.1, size = 3) +
  scale_size_continuous(name = "Child Density") +
  scale_color_brewer(palette = "Set2", name = "Income Quartile") +
  labs(
    title = "Uncovered Children by Income Quantile and Child Density",
    x = "Income Quartile",
    y = "Uncovered Children"
  ) +
  theme_minimal()

ggsave("output/comparison_stats/uncovered_children_density_income.png", plot = p22, width = 8, height = 6)
```


```{r}
# Calculate the average percentage increase in coverage from walking to cycling across all municipalities
sum(joined_covered$pct_increase)/6
```

